We load the data that is normalized and split into train and test and the necessary libraries for the ann model.
```{r ann_load, include=FALSE}
load("../Data/SpotifyTrainTestNorm.Rdata")
library(neuralnet)
library(caret)
```

We build the base model and predict with the base model. 
```{r ann_train, cache=TRUE}
set.seed(12345)
ann_model <- neuralnet(track_popularity ~ ., data = spotify_norm_train, lifesign = "full")
```

To use the confusion matrix to evaluate our model, we change the ann prediction into a binary data, using the median as a threshold. 
```{r ann_confusion}
ann_prediction <- predict(ann_model, spotify_norm_test)
ann_pred_binary <- ifelse(ann_prediction > median(ann_prediction), 1, 0)
ann_confusion <- confusionMatrix(as.factor(ann_pred_binary), as.factor(spotify_norm_test$track_popularity), positive = "1")
ann_confusion
```

The confusion matrix gives us accuracy of `r ann_confusion$overall[1]`and kappa of `r ann_confusion$overall[2]`.

```{r ann_save, include=FALSE}
saveRDS(ann_pred_binary, "../Data/ann_pred.RDS")
saveRDS(ann_prediction, "../Data/ann_prob.rds")
```

