```{r ann_load, include=FALSE}
load("../Data/SpotifyTrainTestNorm.Rdata")
library(neuralnet)
library(caret)
ann_model <- readRDS("../Data/ann_model.rds")
```

## ANN

We build the base model and predict with the base model.
We trained with two hidden layers, the first with 10 node and the second with six.
We also increased the step max so that the model could converge.
The model converged after about 1.26 days of training and 8 million iterations.
```{r ann_train, eval=FALSE}
set.seed(12345)
ann_model <- neuralnet(track_popularity ~ ., data = spotify_norm_train, hidden = c(10, 6), stepmax = 1e9, lifesign = "full")
```

To use the confusion matrix to evaluate our model, we change the ann prediction into a binary data, using the median as a threshold. 
```{r ann_confusion}
ann_prediction <- predict(ann_model, spotify_norm_test)
ann_pred_binary <- ifelse(ann_prediction > median(ann_prediction), 1, 0)
ann_confusion <- confusionMatrix(as.factor(ann_pred_binary), as.factor(spotify_norm_test$track_popularity), positive = "1")
ann_confusion
```

The confusion matrix gives us accuracy of `r ann_confusion$overall[1]`and kappa of `r ann_confusion$overall[2]`.
This accuracy and kappa is not great.

```{r ann_save, include=FALSE}
saveRDS(ann_pred_binary, "../Data/ann_pred.RDS")
saveRDS(ann_prediction, "../Data/ann_prob.rds")
```

