## Data Cleaning

### Clean Data

Cleaning our dataset is crucial for obtaining higher accuracies and kappas by removing unused variables or refactoring existing ones.

```{r data_cleaning lib, include=FALSE}
library(janitor)
```

First we have to read our data.
```{r read_data}
spotify_data <- read.csv("../spotify_songs.csv", stringsAsFactors = T)
```

We then remove all duplicate songs. 
```{r remove_duplicates}
spotify_data <- spotify_data[!duplicated(spotify_data$track_name), ]
summary(spotify_data)
```

We then remove all unnecessary variables such as IDs and names.
```{r remove_variables}
spotify_data$track_id <- NULL
spotify_data$track_album_id <- NULL
spotify_data$playlist_id <- NULL
spotify_data$track_album_release_date <- NULL
spotify_data$track_name <- NULL
spotify_data$track_artist <- NULL
spotify_data$playlist_name <- NULL
spotify_data$track_album_name <- NULL
spotify_data$playlist_subgenre <- NULL # The genre has more general info
```

Next, we change the key variable to a factor.
```{r factorize_key}
spotify_data$key <- as.factor(spotify_data$key)
summary(spotify_data)
str(spotify_data)
```

We change the popularity field to be a binary variable.
Songs that had popularity above the median are 1 and songs below are 0.
By choosing the median, we ensure an almost 50/50 split in the data in terms of popularity.
```{r binary_popularity}
# median is 43 for track popularity
spotify_data$track_popularity <- ifelse(spotify_data$track_popularity >= 43,1,0)
summary(spotify_data$track_popularity)
summary(spotify_data)
```


### Model Matrix

We produce a model matrix to get dummy variables and clean the names of variables. This will help when training our models, as it will remove any issues with column names that could cause our models to fail or produce exceptions in the training and prediction stages.

```{r model_matrix}
spotifymm <- as.data.frame(model.matrix(~ . -1, spotify_data))
spotifymm <- clean_names(spotifymm)
str(spotifymm)
```

### Normalize

We then normalize the data. This will be particularly useful for models like KNN which require normalized data to train.

```{r normalize}
normalize <- function(x) {
  return ((x - min(x)) / (max(x) - min(x))) 
}

spotify_norm <- as.data.frame(lapply(spotifymm, normalize))
summary(spotify_norm)
```

```{r save_clean_data, include=FALSE}
save(spotify_data, spotifymm, spotify_norm, file = "../Data/CleanedData.Rdata")
```
