## Random Forest
```{r rf_load, include=FALSE}
load("../Data/SpotifyTrainTest.RData")
library(randomForest)
library(caret)
```

Building off from our construction of decision trees, random forests work by creating multiple decision trees to use an ensemble approach for making a final model prediction. 

Here, we run the random forest algorithm without any model tuning.
```{r rf_build_base, cache=TRUE}
set.seed(12345)
rf <- randomForest(track_popularity ~ ., data = spotify_train)
rf_base_prediction <- predict(rf, spotify_test)
rf
summary(rf_base_prediction)
```

The base random forest chose a regression tree model.
That means our prediction is not binary.
So we first converted our prediction to a binary variable based on the median prediction and then analyzed the confusion matrix.
```{r rf_base prediction}
rf_base_prediction <- ifelse(0.5207 <= rf_base_prediction, 1, 0)
confusionMatrix(as.factor(rf_base_prediction), as.factor(spotify_test$track_popularity))
```
We can see that our accuracy is a bit low, with an accuracy of 0.615, and our kappa is 0.23.
Our model has some predictive power but not much.

We wanted to improve the model so we set up the tuning parameters for a tuned random forest model.
```{r rf tuning parameters}
ctrl <- trainControl(method = "cv", number = 10,
                     selectionFunction = "oneSE")
grid_rf <- expand.grid(.mtry = c(2, 4, 8, 16))
```

We then trained another random forest model, this time with the tuning.
We chose to optimize kappa.
```{r tuned rf, cache=TRUE}
set.seed(12345)
tuned_rf <- train(as.factor(track_popularity) ~ ., data = spotify_train, method = "rf",
              metric = "Kappa", trControl = ctrl,
              tuneGrid = grid_rf)
```

After, we were able to make a prediction using the tuned random forest model and make a confusion matrix.
```{r tuned rf confusion}
tuned_prediction <- predict(tuned_rf, spotify_test)
confusionMatrix(tuned_prediction, as.factor(spotify_test$track_popularity))
```
The confusion matrix shows that our tuned matrix is very slightly better than the base model but it is mostly the same. Thus, we will use this tuned prediction in the stacked model.

```{r rf_save, include=FALSE}
saveRDS(tuned_prediction, "../Data/rf_tuned_prediction.rds")
```

